<<<<<<< HEAD
---
output: html_document
---
# About the Dataset

```{r echo=FALSE, include=FALSE}
iris <- readRDS("~\\full_run\\data\\iris.rds")
```

**Source:** https://archive.ics.uci.edu/ml/datasets/iris

**Creator:** R.A. Fisher

**Donor:** Michael Marshall (MARSHALL%PLU '@' io.arc.nasa.gov)

## Data Set Information:

```{r iris, eval=TRUE, echo=FALSE, cache=FALSE}
summary(iris)
```

This is perhaps the best known database to be found in the pattern recognition literature. Fisher's paper is a classic in the field and is referenced frequently to this day. (See Duda & Hart, for example.) The data set contains 3 classes of 50 instances each, where each class refers to a type of iris plant. One class is linearly separable from the other 2; the latter are NOT linearly separable from each other.

Predicted attribute: class of iris plant.

This is an exceedingly simple domain.

This data differs from the data presented in Fishers article (identified by Steve Chadwick, spchadwick '@' espeedaz.net ). The 35th sample should be: 4.9,3.1,1.5,0.2,"Iris-setosa" where the error is in the fourth feature. The 38th sample: 4.9,3.6,1.4,0.1,"Iris-setosa" where the errors are in the second and third features.


## Attribute Information:

1. sepal length in cm
2. sepal width in cm
3. petal length in cm
4. petal width in cm
5. class:
* Iris Setosa
* Iris Versicolour
=======
---
output: html_document
---
# About the Dataset

```{r echo=FALSE, include=FALSE}
iris <- readRDS("~\\full_run\\data\\iris.rds")
```

**Source:** https://archive.ics.uci.edu/ml/datasets/iris

**Creator:** R.A. Fisher

**Donor:** Michael Marshall (MARSHALL%PLU '@' io.arc.nasa.gov)

## Data Set Information:

```{r iris, eval=TRUE, echo=FALSE, cache=FALSE}
summary(iris)
```

This is perhaps the best known database to be found in the pattern recognition literature. Fisher's paper is a classic in the field and is referenced frequently to this day. (See Duda & Hart, for example.) The data set contains 3 classes of 50 instances each, where each class refers to a type of iris plant. One class is linearly separable from the other 2; the latter are NOT linearly separable from each other.

Predicted attribute: class of iris plant.

This is an exceedingly simple domain.

This data differs from the data presented in Fishers article (identified by Steve Chadwick, spchadwick '@' espeedaz.net ). The 35th sample should be: 4.9,3.1,1.5,0.2,"Iris-setosa" where the error is in the fourth feature. The 38th sample: 4.9,3.6,1.4,0.1,"Iris-setosa" where the errors are in the second and third features.


## Attribute Information:

1. sepal length in cm
2. sepal width in cm
3. petal length in cm
4. petal width in cm
5. class:
* Iris Setosa
* Iris Versicolour
>>>>>>> 1c81d24d2ac316069c6213d3d2da19ecfd3f6e8e
* Iris Virginica